Generating the Blueprints of the Java Ecosystem

### 2015-02-28 msr.tex
added refs

Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset. It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements. Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculations are available in the database.

% dimitro@bkarak: enrich the above with refs. The ref section is poor. e.g. [...] focuses on object-oriented design metrics *citation here* [...].

>>>>

Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset. It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements. Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics \cite{LOKI94}, \cite{CHKE94}, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity} \cite{cabe76}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculations are available in the database.
